---
title: "GitHub Clone - R Script to Convert Units"
output: html_notebook
---

Source: https://github.com/alexnakagawa/conversionr

This script creates a function called convert_distances to convert between basic imperial and metric units of distance.  The user must specify the quantity of the unit, and which unit to convert from/to.  The function has built in if/e;se-if statements to take multiple written forms of the units, including abbreviations, singular, and plural. The function will throw an error if it cannot handle or recognize the input units. 

Note: Changed original function name from 'conv_dist' to 'convert_distances' for further clarification. 

```{r}
convert_distances <- function(num, from, to) {
  if (from == 'ft' | from == 'feet' | from == 'foot') {
    if (to == 'm' | to == 'meter' | to == 'meters') {
      return(data.frame(num * 0.3048, unit = to))
    } else if (to == 'in' | to == 'inches' | to == 'inch') {
      return(data.frame(num * 12, unit = to))
    } else if (to == 'yd' | to == 'yard' | to == 'yards') {
      return(data.frame(num / 3, unit = to))
    } else if (to == 'mi' | to == 'mile' | to == 'miles') {
      return(data.frame(num * 0.000189394, unit = to))
    } else {
      stop('Invalid desired unit conversion.', call. = FALSE)
    }
  } else if (from == 'yd' | from == 'yard' | from == 'yards') {
    if (to == 'm' | to == 'meter' | to == 'meters') {
      return(data.frame(num * 0.9144, unit = to))
    } else if (to == 'in' | to == 'inches' | to == 'inch') {
      return(data.frame(num * 36, unit = to))
    } else if (to == 'ft' | to == 'feet' | to == 'foot') {
      return(data.frame(num * 3, unit = to))
    } else if (to == 'mi' | to == 'mile' | to == 'miles') {
      return(data.frame(num / 1760, unit = to))
    } else {
      stop('Invalid desired unit conversion.', call. = FALSE)
    }
  } else if (from == 'in' | from == 'inches' | from == 'inch') {
    if (to == 'm' | to == 'meter' | to == 'meters') {
      return(data.frame(num * 0.3048, unit = to))
    } else if (to == 'ft' | to == 'feet' | to == 'foot') {
      return(data.frame(num / 12, unit = to))
    } else if (to == 'yd' | to == 'yard' | to == 'yards') {
      return(data.frame(num / 36, unit = to))
    } else if (to == 'mi' | to == 'mile' | to == 'miles') {
      return(data.frame(num * 1.57828e-5, unit = to))
    } else {
      stop('Invalid desired unit conversion.', call. = FALSE)
    }
  } else if (from == 'mi' | from == 'miles' | from == 'mile') {
    if (to == 'm' | to == 'meter' | to == 'meters') {
      return(data.frame(num * 1609.34, unit = to))
    } else if (to == 'in' | to == 'inches' | to == 'inch') {
      return(data.frame(num * 63360, unit = to))
    } else if (to == 'yd' | to == 'yard' | to == 'yards') {
      return(data.frame(num * 1760, unit = to))
    } else if (to == 'ft' | to == 'feet' | to == 'foot') {
      return(data.frame(num * 5280, unit = to))
    } else {
      stop('Invalid desired unit conversion.', call. = FALSE)
    }
  } else if (from == "m" | from == 'meters' | from == 'meter') {
    if (to == 'ft' | to == 'feet' | to == 'foot') {
      return(data.frame(num * 3.28084, unit = to))
    } else if (to == 'in' | to == 'inches' | to == 'inch') {
      return(data.frame(num * 39.3701, unit = to))
    } else if (to == 'yd' | to == 'yard' | 'yards') {
      return(data.frame(num * 1.09361, unit = to))
    } else if (to == 'mi' | to == 'mile' | to == 'miles') {
      return(data.frame(num * 0.000621371, unit = to))
    } else {
      stop('Invalid desired unit conversion.', call. = FALSE)
    }
  } else {
    stop('Invalid unit type in \'from\'.', call. = FALSE)
  }
}

```


Test the conversion between feet and meters (abbreviated unit inputs)
```{r}
convert_distances(3,'ft','m')
```

Test the conversion between feet and meters (mixture of unit inputs)
```{r}
convert_distances(3,'feet','m')
```

Test the conversion between feet and kilometers (should not work because km, kilometer, kilometers are not desginated units within the function).  Should throw error message specific to "to" units. 

```{r error = TRUE}
convert_distances(3,'feet','km')
```

Test the conversion between kilometers and feet (should not work because km, kilometer, kilometers are not desginated units within the function).  Should throw error message specific to "from" units. 

```{r error = TRUE}
convert_distances(3,'km','ft')
```

